Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-20 article.tex
wording

\textcolor{red}{AJ: It's not clear on which datset we focus on}

@@

Figure \ref{fig:curves} shows the ROC curve and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC.

Two reasons might explain such differences: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator could be reduced to a linear model after
pre-processing. Those results is obviously generalized over the other
datasets see Appendix \textcolor{red}{REF}.

\begin{figure}[bth]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaging method, partial correlation used filer $f_1$).}
\label{fig:curves}
\end{figure}

@@

If the undirected network is perfectly inferred, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small gain.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
Trying to detect the link direction is more penalizing than rewarding.

>>>>

\textcolor{red}{AJ: It's not clear on which dataset we focus on}

@@

Figure \ref{fig:curves} shows the ROC curve  and precision-recall curve
for correlation, GTE and partial correlation on the \textit{normal-2}
dataset. The partial correlation outperforms other state-of-the-art methods
by at least factor of 2 in AUPRC reaching $0.347$ and an increased of $0.05$ in
AUROC. Two reasons might explain such differences: (i) among
those methods only the partial correlation makes the distinction between
direct and indirect connections, (ii) the simulated network from the
\citep{stetter2012model} generator or the neural network in general could be
reduced to a linear model after pre-processing. Those results is obviously
generalized over the other datasets see Appendix \textcolor{red}{REF}.

From the pre-processing to the weighted averaging of partial correlation
matrix, all pre-processing and post-processing is useful to improve score

\begin{figure}[bth]
\centering
\subfigure[ROC curves]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[Precision-recall curves]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{The weighted average of partial correlation matrix, winning approach
         of the challenge, yields better than AUROC and AUPRC than all
         other state-of-the-art methods. (parameters: $\tau=0.11$ except for
         averaging method, partial correlation used filter $f_1$).}
\label{fig:curves}
\end{figure}

@@

If the undirected network is perfectly inferred, it would already yield
high AUROC score for instance $\approx{}0.996$ on \textit{normal-1}. Trying
to infer edge directivity is likely to be counter-productive or yield
small gain.
By contrast, the same experiment with AUPRC would yield
to a score of $\approx 0.789$ on \textit{normal-1}. Thus inferring
correctly directivity would be more rewarding in AUPRC term.
Interestingly, methods that takes into account directivity, namely GTE and
GENIE3, improve their AUROC and AUPRC by giving the same way to directed edges.
(see GTE and GTE(undirected) in Figure \ref{fig:curves}
\textcolor{red}{AJ: Figure \ref{fig:curves}  contradicts this message,
especially pr-curve.}).
Trying to detect the link direction is more penalizing than rewarding.
